RadLib: a radiative heat transfer model library for CFD

### 2021-03-24 submissions/CPC_response_to_reviewers.md

	**In order to avoid subjective language, this sentence has been revised as follows: "RadLib's modular framework can also accomodate new models, . . .". Specific extensibility issues are addressed below with their respective reviewer comments.**

4.There are several minor issues that need to be addressed:

	1. Abstract: “well-written” is subjective and should be removed.

	**The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**

	2.Introduction: second sentence: “Combustion simulations…” is a run-on sentence.

	**Technically, no, this is not a run-on sentence, but its structure is awkward and inhibits readability. It has been revised to the following: "For example, combustion simulations are often complicated by the need for accurate radiation modeling, which can be difficult to implement and computationally expensive relative to overall simulation cost."**

    3. Page 10: “[INSERT RUNTIME COMPARISONS HERE]”

@@

	**Fixed section heading. Now correctly reads "Declaration of Competing Interests".**

### Software deficiencies & suggestions:

1. API doxygen documentation is non-standard. It appears that the doxygen documentation is provided in the .cc files rather than the header files, which is where it is typically found. Downstream developers would typically be working from headers and the installed library, so it is convention to have doxygen documentation in the header only. This also reduces clutter in the implementation files.

	**The authors were previously unaware of any such standards or conventions, and follow up research indicates that this is a stylistic preference rather than a flaw in the software. The locations of doxygen documentation blocks were chosen for overall readability as they tended to clutter the header files and were less obtrusive when located in the implementation files. However, the reviewer does make a valid point regarding usage by downstream developers, and while we would expect the typical RadLib user to be comfortable working with both header files and source code, it is worthwhile to consider all possible usages. Because this is an issue of style rather than function, no immediate changes have been made to the code or its documentation, but the authors appreciate this information about standard practice and will consider its implications moving forward.**

@@

2. make_examples.sh:
    1.	will only work with a g++ compiler in the user’s path.
    1.	Is referred to as build_examples.sh in the README.md file
    1.	is redundant with the cmake build system and isn’t portable. It should probably be removed.
3. It appears that there are no tests associated with the library. This is a bit surprising - I would expect regression test coverage on the basic API functionality.
4. CMake build system:
    1.	Consider installing a “RadLib.cmake” file for downstream usage by CMake-based projects. This helps downstream build systems configure for RadLib usage (setting include paths, etc.).
    1.	probably shouldn’t specify optimize or debug flags directly, as CMake will provide appropriate values on most platforms.
    1.	the default build type isn’t defaulting to Release for me; it remains blank.
    1.	I suggest not using verbose makefiles by default.
    1.	Using GLOB to install the headers is not the appropriate CMake approach.
    1.	the data files are not copied into the examples build directory, meaning that the example executables do not run.
    1.	The run-examples.sh script is not helpful as it is not installed into the build directory where the executables are produced and doesn’t have path information to actually run the executables.
    1.	Using “doxygen” as a target is not ideal since it conflicts with the “doxygen” executable name. It still works fine though...

5. It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker.

	**At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software. The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance. The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library, however. The authors appreciate the suggestion and will consider it for future development.**

@@

6. It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits? Same for WSGG. There is no discussion of why this was chosen, how the coefficients were determined, or a characterization of its accuracy. Do you observe any problematic behavior with the fourth order polynomials over temperatures from 300 to 3000 K?  Are these interpolants or regression of data?

	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models. All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]). The authors believe that this is an issue of scope rather than missing information, but they are willing to extend the discussion at the editor's discretion.**

@@

7. The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits. And given that this process is opaque, it isn’t reproducible.

8. RadLib only considers CO2 and H2O for WSGG, which is fairly limited. Even for Plank mean, only H2O, CO2, CO and CH4 are considered. NO and OH would be nice to include. It appears that including additional species would be a non-trivial undertaking.

	**All WSGG correlations consider only CO2-H2O mixtures with the exception of specialized subset of WSGG models that consider CO2-H2O-soot mixtures. This WSGG model was chosen for RadLib due to its popularity, relative simplicity, and good performance. Note that WSGG models usually address radiation in combustion environments. RadLib implements the WSGG model presented by Bordbar et al. in references [10] and [11], which was developed specifically for use in oxy-fired combustion simulations. CO2 and H2O are the major products of all combustion processes, and CO is a major product of rich combustion. NO and OH are minor species that, while important to other aspects of combustion processes, do not typically participate significantly in radiative heat transfer processes. For more information, please refer to Section 20.6 of reference [2] and/or Section 3.4.1 of *Radiative Heat Transfer in Turbulent Combustion Systems* by Modest and Haworth.**

	**It should also be noted that the Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations. This is why Section 2.1 explicitly references the TNF radiation model and its calculated Planck Mean absorption coefficients. As implemented, the model is not intended to be general or extensible to other gas species and was never presented as such. Adding additional species would indeed be a non-trivial undertaking, but that is neither the goal nor purpose of RadLib as a software package, which presents and validates models rather than evaluating them.**

@@

	**This was a placeholder statement that should not have been included in the document. It has been removed.**

3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?

4. Equation 6 appears to be inaccurate.

	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations near it. **

### 2021-03-26 submissions/CPC_response_to_reviewers.md

    3. These kinds of statements persist throughout the second paragraph as well. There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc. The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.

3. Section 5 claims that “RadLib’s modular framework is designed to easily accommodate new models as well,” which is a bit of an overstatement. See comments below w.r.t. assumptions on species considered, hard-coded polynomial coefficients, etc. all of which reduce extensibility.

	**In order to avoid subjective language, this sentence has been revised as follows: "RadLib's modular framework can also accomodate new models, . . .". Specific extensibility issues are addressed below with their respective reviewer comments.**

4. There are several minor issues that need to be addressed: 
	1. Abstract: “well-written” is subjective and should be removed.

@@

		**The offending sentence (actually located in the "Solution method" section of the Program Summary) has been revised to eliminate subjective language.**

	2. Introduction: second sentence: “Combustion simulations…” is a run-on sentence.

@@

5. It appears that line-by-line data from HITEMP/HITRAN files cannot be loaded into RadLib. That’s an unfortunate limitation, but not a deal-breaker.

	**At present, RadLib's models cannot accommodate such data input, but this is a limitation of the models themselves, not the software. The appropriate line-by-line data is included within the RadLib package, which the authors consider a convenience rather than a hindrance. The ability to load database files directly into RadLib could be useful to researchers looking to extend RadLib's model library, however. The authors appreciate the suggestion and will consider it for future development.**

6. It looks like the software hard-codes Plank mean absorption coefficients as (fourth-order?) polynomial fits? Same for WSGG. There is no discussion of why this was chosen, how the coefficients were determined, or a characterization of its accuracy. Do you observe any problematic behavior with the fourth order polynomials over temperatures from 300 to 3000 K?  Are these interpolants or regression of data?

	**This discussion was purposely omitted because it does not align with the goal of the paper, which is to present RadLib as a software tool for calculating radiation property data, not to evaluate or compare the included models. All of the reviewer's questions are addressed in detail in the referenced literature (Planck Mean coefficients in [3,5] and WSGG in [10,11]). The authors believe that this is an issue of scope rather than missing information but are willing to extend the discussion at the editor's discretion.**

@@

7. The two previous items combined lead to a significant limitation of RadLib: one cannot easily add new species or modify existing data that is used to generate the absorption coefficients since there has been internal preprocessing of (an unknown subset of) the HITEMP/HITRAN databases to produce curve fits. And given that this process is opaque, it isn’t reproducible.

	**The authors acknowledge that modifying existing models in RadLib is non-trivial, but would like to note that the paper does not claim that the implemented models are easily modified, only that the RadLib framework can be used to implement and validate additional models. Additionally, the authors disagree with the reviewer's statement regarding opacity and reproducability. The referenced literature (see above) clearly outlines the data sources and preprocessing methods applied; this information was omitted from the current paper for the reasons stated above. Given the provided sources, the process is neither opaque nor non-reproducible.**

@@

## Reviewer 2

A radiation spectral property library is developed in this study using C++. A Planck-mean absorption coefficient based model, a WSGG model and a RCSLM model from the literature are implemented  in the package. Verification results are presented and discussed. Although the authors addressed an important issue of radiation modeling, the contribution is marginal in the reviewer's opinion. No new models/methods are proposed in this study. As the authors correctly pointed out, the solver for radiative transfer equation is equally important, which is not included in the library. The coupling of a spectral model to a specific RTE solver, can have different levels of challenges depending on the combination. The design of the library doesn't really address any of the RTE-related issues, nor provide any new solutions to simplify the coupling of spectral models to RTEs. If the authors can demonstrate that the library can be coupled with popular CFD software and popular RTE solvers such as P1 and DOM, it would further improve the quality of this study. A few other concerns are listed as follows:

1. RADCAL data were used to generate the PlanckMean absorption coefficient. Based on the reviewer's experience, the PlanckMean absorption coefficients can have meaningful differences when generated from RADCAL and from HiTEMP2010. It is recommended a more recent database being used for the library.

	**The Planck Mean absorption coefficients model as implemented in RadLib refers specifically to the radiation model in [3,5], which is one of the most common radiation models applied to turbulent combustion simulations. It was chosen because of its popularity and widespread use in combustion simulations (despite its limitations). That said, there is value in using the most current tools. Given the reviewer's experience with variance in the Planck Mean absorption coefficients as calculated from various databases, the authors will strongly consider adding an updated Planck Mean model using the most current available data.**

@@

	**This was a placeholder statement that should not have been included in the document. It has been removed.**

3. In Figure 2, the RCSLM seems to consistently perform better than WSGG, except in Example S2. In addition, WSGG performs worse than PM in Example S4. Can the authors explain why?

4. Equation 6 appears to be inaccurate.

	**Upon review, the authors find no errors in Equation 6, which matches Equation 20.65 of the general band model (of which the WSGG model is a subset) derivation in [2] and appears to be consistent with the other equations in the paper.**

@@

**TO DO: add something to introduction to address this**

3) RadLib is intended to be expanded with new radiation property models in the future and interfaced with a user-supplied solver module for RTE. A brief discussion on how to interface such an external solver module should be presented. There is an example of a ray-tracing solver presented in the code files, but a brief discussion on coupling one's own RTE solver is important in the manuscript. Additionally, a brief discussion on how a user can add a new radiative property model should also be included.

4) The Planck-mean absorption coefficient included in RadLib is based on TNF workshop data (from 2003). According to the references cited, these are fairly old correlations. If the authors use these data, I am concerned that the model parameters and correlations used in RadLib for the PM model may be obsolete and inaccurate. Can the authors please comment on this?

	**The authors purposely chose the TNF workshop data for calculating Planck Mean absorption coefficients because it is one of the most common and widely used radiation models applied to turbulent combustion simulations, despite its age and limitations. The paper includes a brief discussion on the limited applicability of this model, especially for combustion simulations, and demonstrates its deficiencies in the example cases. It is true that this model is neither current nor particularly accurate, and the authors are strongly considering adding an updated Planck Mean model using the most current available data.**

	**TO DO: add discussion to address the age of the model and why we chose to include it anyway**

@@

3) In Page 2, "In some cases, radiative gains or losses are small compared to other energy sources or heat transfer modes and radiation can be safely neglected, ... difficult to simulate accurately without a robust radiation model." Please provide some references to support these arguments.

**TO DO: add requested references**

4) Please explain all the symbols used in equations. For example, eta in Eqn. 1 (and subsequent equations), Eb  in Eqn. 11.

**TO DO: explain and/or list equation symbols not already addressed**

@@

5) Page, 4: "Global models are an important class of radiation property models that make use of spectrally-integrated radiation properties and are usually versions of the weighted sum of gray gases (WSGG) model [1, 2]." This sentence is somewhat misleading. It may be more appropriate to think of WSGG models as special cases of SLW or FSK models.

	**The authors agree that this statement could be potentially misleading. The second half of the sentence (beginning with ". . .and are usually. . .") has been removed.**

6) In lines 48-52 on Page 4, the authors say that the absorption coefficients are calculated using some correlations after some curve-fitting to spectroscopic databases. I am not sure what the authors refer to as correlations. There may be some correlations involved in WSGG models, but it is not clear to me where are correlations involved in RCSLW.

	**The RCSLW model's key tool is the absorption line blackbody distribution function (ALBDF), which is calculated using sppectral data available from databases like HITEMP. This is discussed briefly at the end of Section 2.3 on pages 8-9. For more information on how spectral data is used to calculate the ALBDFs, please see reference [22].**

### 2021-03-30 submissions/CPC_response_to_reviewers.md

This manuscript introduces “RadLib,” a C++ library to calculate absorption coefficients for use in radiative heat transfer calculations. The library has reasonable value to the research community, despite a few limitations in its scope and design. The library is self-contained (doesn’t have any external dependencies), which is convenient.

I have a number of comments on the manuscript as well as the software itself which the authors should consider to improve the manuscript and software.

### Manuscript:
1.There is no general user documentation provided in section 3. Figure 1 includes information that is more algorithmic than illustrative of the API.

2. Section 5 makes several editorial claims that are quite subjective, and not well-supported:
	1. First sentence: “historically difficult to implement … complexity and high computational costs”
		-Property evaluation is not the expensive part of a radiation calculation. Solving the RTE is the expensive part.
        	-I wouldn’t characterize the property evaluation as particularly complex in comparison with other aspects of combustion simulations (kinetics, thermodynamics, transport properties).

@@

    2. At the end of the first paragraph, the authors seem to imply that RadLib will solve the challenges of radiation modeling. Again, it is the RTE solver, not the property evaluation, that is the largest time-sink in terms of computer and human resources.

    3. These kinds of statements persist throughout the second paragraph as well. There are limitations in RadLib such as lack of scattering treatment for particle-laden flows, inability to include more species, lack of any line-by-line capabilities, etc. The library checks a few useful boxes, but the verbiage here seems to take more credit than the authors may be due.

    **The authors have a number of concerns about the reviewer's claims here that they would like to address. First, note that the subject of the first sentence of Section 5 is "radiative heat transfer models", which does not refer specifically to either radiation property models or RTE evaluation methods, but the treatment of computational radiative heat transfer as a whole. This generalization holds for the entire first paragraph of Section 5. Additionally, at no point in the paper do the authors claim that property evaluation is more complex or computationally expensive than the RTE solution, only that it "can be a difficult and time-consuming portion of radiation calculations" (pg. 2). Likewise, the paper contains no claims about the complexity of radiation property models in relation to other aspects of combustion simulations. (On this topic, however, the authors would like to point out that these other aspects of combustion simulations are typically well-characterized in both commercial and open-source CFD codes and do not require very much user interaction, whereas radiation modeling is often absent or highly simplified.) The second paragraph of Section 5 is a brief discussion on how RadLib can benefit researchers that draws from the authors' experiences. It does not claim that RadLib will solve any of the challenges of radiation modeling, only that it can "ease . . . obstacles", which the authors believe it can do.**

    **All of that said, however, the fact that the reviewer made these assumptions and pointed out these implications indicates that the paper's language is, in fact, too subjective. Even though none of these statements were explicitly made, they must be implied for the reviewer to come to these conclusions. As such, revisions have been made throughout the paper to reduce subjective language, support generalized statements with additional explanation and/or references, and include due discussion of RadLib's limitations.**

### 2021-04-07 manuscript/manuscript.tex
Adding to section 3 to include more information on user interaction with the RadLib library according to reviewer comments.

RadLib installation is automated with CMake. First, navigate to the \texttt{radlib/build} directory. If the user requires an installation location other than the default \texttt{radlib/installed} directory, edit the \texttt{user\textunderscore config} file before running CMake. To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}. Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process. The generated C++ library file is located at \texttt{radlib/installled/lib/libradlib.a}.

Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry, making it a versatile tool for any simulation that requires radiative heat transfer, regardless of configuration. The interfaces, solver, and examples included with the library serve to illustrate its use and validate the implementation and results. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

>>>>

RadLib installation is automated with CMake. First, navigate to the \texttt{build} directory. If the user requires an installation location other than the default \texttt{installed} directory, edit the \texttt{user\textunderscore config} file before running CMake. To compile the package, run the command \texttt{cmake -C user\textunderscore config ../source}. Upon successful completion, run \texttt{make} and then \texttt{make install} to complete the process. To use RadLib in C++ projects, include the generated C++ library file, located at \texttt{installled/lib/libradlib.a}, and/or header files, located in \texttt{installed/include}, according to the project's build scheme. To use RadLib in Python, update the system \texttt{PYTHONPATH} environment variable and import the module, named \texttt{pyrad}, into the project.

The interfaces, solver, and examples included with the library serve to demonstrate its use and validate the implementation and results. Figure \ref{fig:flowchart} illustrates the basic structure use of the RadLib package within a generic example using the provided interfaces. The RadLib library generates absorption coefficients and their weighting factors for use within the appropriate RTE, but does not specify any particular geometry. After creating a radiation object, users interact with RadLib through the \texttt{get\textunderscore k\textunderscore a()} function, which requires arguments corresponding to the system temperature; system pressure; species mass fractions for H$_2$O, CO$_2$, CO, and CH$_4$; soot volume fraction in units of parts per million (ppm), if applicable; and variables initialized to receive output values for the radiation absorption coefficients and their corresponding weights. For examples that illustrate how a user might interact with RadLib, refer to the \texttt{simple\textunderscore interface.cc} and \texttt{simple\textunderscore interface.py} example files located in the \texttt{examples/c++} and \texttt{examples/python} folders, respectively. 
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%
